The hedging hyperprior for the normal distribution: unknown mean, unknown precision

### 2023-03-21 text/23/normal-hedging-hyperprior-part-1.Rmd
Started work on normal-hedging-hyperprior-part3

The parameter $\tau$ is called the precision. Note that some define the precision differently as the inverse of the standard deviation rather than the inverse of the variance,

Assume that $\tau$ is known and equal to $\tau_F$. A more general case, with $\tau$ unknown is described on a separate web page. For simplicity, we will drop any multiplicative constants not involving X or $\theta$

>>>>

The parameter $\tau$ is called the precision. Note that some define the precision differently as the inverse of the standard deviation rather than the inverse of the variance.

Assume that $\tau$ is known and equal to $\tau_F$. Other cases with [mean known and precision unknown][sim2] and with [both mean and precision unknown][sim3] appear on a different web pages.

[sim2]: http://new.pmean.com/normal-hedging-hyperprior-part2
[sim3]: http://new.pmean.com/normal-hedging-hyperprior-part3

For simplicity, we will drop any multiplicative constants not involving X or $\theta$

### 2023-03-21 text/23/normal-hedging-hyperprior-part-3.Rmd
Started work on normal-hedging-hyperprior-part3

---
title: "The hedging hyperprior for the normal distribution: known mean, unknown precision"
source: "New"
date: "2023-03-14"
categories:
- Blog post
tags:
- Bayesian statistics
output: html_document
---

@@

$f(X; \mu, \theta) = \sqrt{\frac{\theta}{2 \pi}}e^{-\frac{1}{2}\theta (X-\mu)^2}$

where

$\theta=\frac{1}{\sigma*2}$

Assume that the mean of the normal distribution, $\mu$, is known and equal to $\mu_F$. An earlier case with precision known and the mean  unknown appears on a different web page. A more general case, with both the mean and the precision of the normal distribution unknown is also described on a separate web page. For simplicity, we will drop any multiplicative constants not involving X or $\theta$

$f(X; \theta) \propto \sqrt{\theta}e^{-\frac{1}{2}\theta(X-\mu_F)^2}$

The conjugate prior for a normal distribution is a gamma distribution.

$g(\theta; \alpha_0, \beta_0) = \frac{\beta_0^{\alpha_0}}{\Gamma(\alpha_0)} \theta^{\alpha_0-1} e^{-\beta_0 \theta}$

Set the prior parameters to

$\alpha_0=n_0$

$\beta_0 = n_0 \theta_0$

and remove any multiplicative constants with respect to $\theta$ to get

$g(\theta; n_0, \theta_0) \propto \theta^{n_0-1} e^{-n_0 \theta_0 \theta}$

In this parameterization, $n_0$ is the prior sample size.

>>>>

---
title: "The hedging hyperprior for the normal distribution: unknown mean, unknown precision"
source: "New"
date: "2023-03-21"
categories:
- Blog post
tags:
- Bayesian statistics
output: html_document
---

@@

$f(X; \mu, \tau) = 
  \sqrt{\frac{\tau}{2 \pi}}
  e^{-\frac{1}{2}\tau (X-\mu)^2}$

Assume that both the mean and the precision of the normal distribution are unknown. Earlier cases with [mean unknown and precision known][sim1] and with [mean known and precision unknown][sim2] appear on a different web pages.

[sim1]: http://new.pmean.com/normal-hedging-hyperprior-part1
[sim2]: http://new.pmean.com/normal-hedging-hyperprior-part2

For simplicity, we will drop any multiplicative constants not involving X, $\mu$, or $\tau$.

$f(X; \mu, \tau) \propto 
  \sqrt{\tau}
  e^{-\frac{1}{2}\tau(X-\mu)^2}$

With two unknown parameters, you need two prior distributions. The prior distribution for $\tau$ is

$k(\tau) = 
  \frac{(n_0 \tau_0)^{n_0}}{\Gamma(n_0)}
  \tau^{n_0-1}
  e^{-\beta_0 \tau}$

which is a gamma distribution with

$\alpha=n_0$ and $\beta=n_0\tau_0$

Use a conditional prior for $\mu$ given $\tau$.

$g(\mu | \tau) =
  \sqrt{\frac{\tau}{2 \pi}}
  e^{-\frac{1}{2}\tau (\mu-\mu_0)^2}$

You can get an unconditional prior for $\mu$ by integrating out the prior on $\tau$

$g(\mu) = \int
  \sqrt{\frac{\tau}{2 \pi}}
  e^{-\frac{1}{2}\tau (\mu-\mu_0)^2}
  \frac{(n_0 \tau_0)^{n_0}}{\Gamma(n_0)}
  \tau^{n_0-1}
  e^{-\beta_0 \tau}d\tau$

Pull out any multiplicative constants not involve $\tau$.

$g(\mu) = 
  \frac{1}{\sqrt{2 \pi}}
  \frac{(n_0 \tau_0)^{n_0}}{\Gamma(n_0)}
  \int\tau^{n_0-\frac{1}{2}}
  e^{-\tau(\frac{1}{2} (\mu-\mu_0)^2-\beta_0)}
  d\tau$
